{ \fontfamily{ptm}\selectfont Nesterov's First Order Method Accelerations: Unification, Applications and Numerical Experiments }

### 2025-02-10 Notebook LaTEX/Proposal/proposal.tex
>w<, changes

            Removing the smoothness assumption of $F$, $\mathbb M$ solves subproblem $\mathcal M_{\kappa^{-1}F}(\cdot, y_k)$ which is only strongly convex.

@@

            Unfortunately it is nontrivial to see it as true because $\mathbb A$ optimizes Moreau Envelope $\mathcal M^*_{\kappa^{-1}F}(x)$ through inexact evaluation and the Moreau Envelope has Lipschitz gradient. 
            For $\mathbb A$ Theorem 3.2.1 doesn't apply. 
            So, here is the refined question: 

>>>>

            Removing the smoothness assumption of $F$, then $\mathbb M$ solves $\mathcal M_{\kappa^{-1}F}(\cdot, y_k)$ which is $\kappa > 0$ strongly convex.

@@

            Unfortunately it doesn't apply because $\mathbb A$ optimizes Moreau Envelope $\mathcal M^*_{\kappa^{-1}F}(x)$ through inexact evaluation and the Moreau Envelope has Lipschitz gradient. 
            Here is the refined question: 
